Untitled

### 2020-06-30 Thesis_Chapter_1/Supp_Material.tex
Supp. mat

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{setspace}\doublespacing
\usepackage{float}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

\textbf{Authors:} Jose B. Lanuza, Ignasi Bartomeus, Tia Lynn Ashman,
Romina Rader

@@

\textbf{Table S4.} Species x species matrix with the significance of
effect ``yes'' or ``no'' of the different donors on the seed set of the
different recipient species.

\textbf{Table S5.} Estimates, standard error, t-value and P-value of the
effect of the different 9 donors on each recipient species.

\textbf{Table S6.} Number of seeds produced with 100\% foreign pollen
treatments for the different recipient species.

\textbf{Table S7.} Phylogenetic signal and significance for all the
different traits

\textbf{Table S8.} Procrustes analysis results.

@@

\#TABLE S1 \begingroup\fontsize{7}{9}\selectfont

\begin{longtabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X}
\toprule
\textbf{Species} & \textbf{Common\_names} & \textbf{Variety} & \textbf{Source}\\
\midrule
\endfirsthead
\multicolumn{4}{@{}l}{\textit{(continued)}}\\
\toprule
Species & Common\_names & Variety & Source\\
\midrule
\endhead
\
\endfoot
\bottomrule
\endlastfoot
\rowcolor{gray!6}  Brassica oleracea & Wild cabbage & Capitata & https://www.mrfothergills.com.au/\\
\addlinespace
Brassica rapa & Pak choi & Chinensis & https://www.mrfothergills.com.au/\\
\addlinespace
\rowcolor{gray!6}  Eruca sativa & Rocket &  & https://www.mrfothergills.com.au/\\
\addlinespace
Sinapis alba & White mustard &  & https://www.mrfothergills.com.au/\\
\addlinespace
\rowcolor{gray!6}  Ipomoea aquatica & Water spinach &  & https://www.theseedcollection.com.au/\\
\addlinespace
Ipomoea purpurea & Morning glory &  & http://www.shaman-australis.com.au\\
\addlinespace
\rowcolor{gray!6}  Capsicum annuum & Capsicum & California Wonder & https://www.edenseeds.com.au\\
\addlinespace
Petunia integrifolia & Petunia &  & https://www.dianeseeds.com/\\
\addlinespace
\rowcolor{gray!6}  Solanum lycopersicum & Tomato & Tommy Toe & https://www.mrfothergills.com.au/\\
\addlinespace
Solanum melongena & Eggplant & Little Fingers & https://www.4seasonsseeds.com.au/\\*
\end{longtabu}
\endgroup{}

@@

TABLE S2
\begingroup\fontsize{6}{8}\selectfont

\resizebox{\linewidth}{!}{
\begin{tabu} to \linewidth {>{\raggedright\arraybackslash}p{2cm}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
\toprule
\textbf{Species} & \textbf{Pollen size $\mu$m} & \textbf{Pollen grains per anther} & \textbf{Ovule number} & \textbf{Pollen:ovule ratio} & \textbf{Stigma area $\mu$m$^{2}$} & \textbf{Stigma length (mm)} & \textbf{Stigma width (mm)} & \textbf{Style length (mm)} & \textbf{Style width (mm)} & \textbf{Ovary length (mm)} & \textbf{Ovary width (mm)} & \textbf{Selfing rate} & \textbf{SI index}\\
\midrule
\rowcolor{gray!6}  Brassica oleracea & 27.72 & 42033 & 29 & 8696.48 & 0.62 & 0.53 & 0.88 & 2.32 & 0.65 & 5.93 & 1.11 & 0.0 & 0.00\\
\addlinespace
Brassica rapa & 25.35 & 7133 & 26 & 1646.08 & 0.36 & 0.37 & 0.73 & 1.08 & 0.52 & 3.53 & 0.88 & 0.0 & 0.00\\
\addlinespace
\rowcolor{gray!6}  Capsicum annuum & 32.46 & 30761 & 241 & 765.83 & 1.06 & 0.72 & 1.18 & 3.24 & 1.06 & 3.15 & 5.80 & 0.8 & 0.64\\
\addlinespace
Eruca versicaria & 24.95 & 22151 & 24 & 5537.75 & 0.35 & 0.73 & 0.67 & 6.60 & 0.73 & 4.42 & 0.94 & 0.1 & 0.02\\
\addlinespace
\rowcolor{gray!6}  Ipomoea aquatica & 70.10 & 858 & 4 & 1072.50 & 3.26 & 1.43 & 2.25 & 19.44 & 0.45 & 2.38 & 1.42 & 0.6 & 0.75\\
\addlinespace
Ipomoea purpurea & 97.59 & 654 & 6 & 545.00 & 2.27 & 1.24 & 1.88 & 28.23 & 0.58 & 1.06 & 1.57 & 1.0 & 2.74\\
\addlinespace
\rowcolor{gray!6}  Petunia integrifolia & 24.74 & 34657 & 220 & 787.66 & 1.17 & 0.80 & 1.32 & 14.65 & 0.45 & 3.13 & 1.77 & 0.9 & 0.26\\
\addlinespace
Sinapis alba & 33.59 & 3507 & 6 & 3507.00 & 0.55 & 0.63 & 0.91 & 3.62 & 0.77 & 1.98 & 1.07 & 0.7 & 1.12\\
\addlinespace
\rowcolor{gray!6}  Solanum lycopersicum & 22.00 & 28915 & 92 & 1885.76 & 0.09 & 0.19 & 0.35 & 6.47 & 0.31 & 1.16 & 1.13 & 0.7 & 0.48\\
\addlinespace
Solanum melongena & 25.18 & 166989 & 1010 & 992.01 & 1.14 & 0.96 & 1.33 & 11.33 & 0.94 & 4.02 & 3.55 & 1.0 & 1.45\\
\bottomrule
\end{tabu}}
\endgroup{}

@@

TABLE S3 \begingroup\fontsize{6}{8}\selectfont

\resizebox{\linewidth}{!}{
\begin{tabu} to \linewidth {>{\raggedright\arraybackslash}p{2cm}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
\toprule
\textbf{Species} & \textbf{Hand cross-pollination} & \textbf{Hand self-pollination} & \textbf{Spontaneous selfing} & \textbf{Apomixis}\\
\midrule
\rowcolor{gray!6}  Brassica oleracea & 32.07 & 0.00 & 0.00 & 0\\
\addlinespace
Brassica rapa & 44.97 & 0.00 & 0.00 & 0\\
\addlinespace
\rowcolor{gray!6}  Capsicum annuum & 80.00 & 56.47 & 19.34 & 0\\
\addlinespace
Eruca sativa & 23.75 & 0.42 & 0.00 & 0\\
\addlinespace
\rowcolor{gray!6}  Ipomoea aquatica & 40.00 & 30.00 & 20.00 & 0\\
\addlinespace
Ipomoea purpurea & 31.67 & 86.67 & 31.67 & 0\\
\addlinespace
\rowcolor{gray!6}  Petunia integrifolia & 80.16 & 24.77 & 0.00 & 0\\
\addlinespace
Sinapis alba & 41.67 & 48.33 & 5.00 & 15\\
\addlinespace
\rowcolor{gray!6}  Solanum lycopersium & 85.65 & 41.20 & 68.48 & 0\\
\addlinespace
Solanum melongena & 60.48 & 74.87 & 21.56 & 0\\
\bottomrule
\end{tabu}}
\endgroup{}

@@

\begin{figure}
\centering
\includegraphics{Supp_Material_files/figure-latex/unnamed-chunk-4-1.pdf}
\caption{\textbf{Fig. S1} Average number of pollen grains per stigma for
20 different treatments (3 replicates per tratment). For each treatment,
we show the average number of conspecific pollen grains (grey) and
heterospecific pollen grains (light blue) per stigma. For each pair of
species on the x-axis, the first species is the recipient species, and
the second, the donor species.}
\end{figure}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{setspace}\doublespacing
\usepackage{float}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

\textbf{Authors:} Jose B. Lanuza, Ignasi Bartomeus, Tia-Lynn Ashman,
Romina Rader

@@

\textbf{Table S4.} Estimates, standard error, t-value and P-value of the
effect of the different 9 donors on each recipient species.

\textbf{Table S5.} Number of seeds produced with 100\% foreign pollen
treatments for the different recipient species.

\textbf{Table S6.} Phylogenetic signal and significance for all the
different traits

\textbf{Table S7.} Procrustes analysis results.

@@

\begingroup\fontsize{7}{9}\selectfont

\begin{longtabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X}
\caption{\label{tab:unnamed-chunk-1}\textbf{Table S1.} Species names, common names, varieties and sources of the different seeds.}\\
\toprule
\textbf{Species} & \textbf{Common\_names} & \textbf{Variety} & \textbf{Source}\\
\midrule
\endfirsthead
\caption[]{\textbf{Table S1.} Species names, common names, varieties and sources of the different seeds. \textit{(continued)}}\\
\toprule
Species & Common\_names & Variety & Source\\
\midrule
\endhead
\
\endfoot
\bottomrule
\endlastfoot
\rowcolor{gray!6}  Brassica oleracea & Wild cabbage & Capitata & https://www.mrfothergills.com.au/\\
\addlinespace
Brassica rapa & Pak choi & Chinensis & https://www.mrfothergills.com.au/\\
\addlinespace
\rowcolor{gray!6}  Eruca sativa & Rocket &  & https://www.mrfothergills.com.au/\\
\addlinespace
Sinapis alba & White mustard &  & https://www.mrfothergills.com.au/\\
\addlinespace
\rowcolor{gray!6}  Ipomoea aquatica & Water spinach &  & https://www.theseedcollection.com.au/\\
\addlinespace
Ipomoea purpurea & Morning glory &  & http://www.shaman-australis.com.au\\
\addlinespace
\rowcolor{gray!6}  Capsicum annuum & Capsicum & California Wonder & https://www.edenseeds.com.au\\
\addlinespace
Petunia integrifolia & Petunia &  & https://www.dianeseeds.com/\\
\addlinespace
\rowcolor{gray!6}  Solanum lycopersicum & Tomato & Tommy Toe & https://www.mrfothergills.com.au/\\
\addlinespace
Solanum melongena & Eggplant & Little Fingers & https://www.4seasonsseeds.com.au/\\*
\end{longtabu}
\endgroup{}

@@

\begin{table}

\caption{\label{tab:unnamed-chunk-2}\textbf{Table S2.} Measurements ($\bar{X}$ ± SD) for all the 13 different traits for all plant species.}
\centering
\resizebox{\linewidth}{!}{
\fontsize{6}{8}\selectfont
\begin{tabu} to \linewidth {>{\raggedright\arraybackslash}p{2cm}>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X>{\raggedleft}X}
\toprule
\textbf{Species} & \textbf{Pollen size $\mu$m} & \textbf{Pollen grains per anther} & \textbf{Ovule number} & \textbf{Pollen:ovule ratio} & \textbf{Stigma area $\mu$m$^{2}$} & \textbf{Stigma length (mm)} & \textbf{Stigma width (mm)} & \textbf{Style length (mm)} & \textbf{Style width (mm)} & \textbf{Ovary length (mm)} & \textbf{Ovary width (mm)} & \textbf{Selfing rate} & \textbf{SI index}\\
\midrule
\rowcolor{gray!6}  Brassica oleracea & 27.72 & 42033 & 29 & 8696.48 & 0.62 & 0.53 & 0.88 & 2.32 & 0.65 & 5.93 & 1.11 & 0.0 & 0.00\\
\addlinespace
Brassica rapa & 25.35 & 7133 & 26 & 1646.08 & 0.36 & 0.37 & 0.73 & 1.08 & 0.52 & 3.53 & 0.88 & 0.0 & 0.00\\
\addlinespace
\rowcolor{gray!6}  Capsicum annuum & 32.46 & 30761 & 241 & 765.83 & 1.06 & 0.72 & 1.18 & 3.24 & 1.06 & 3.15 & 5.80 & 0.8 & 0.64\\
\addlinespace
Eruca versicaria & 24.95 & 22151 & 24 & 5537.75 & 0.35 & 0.73 & 0.67 & 6.60 & 0.73 & 4.42 & 0.94 & 0.1 & 0.02\\
\addlinespace
\rowcolor{gray!6}  Ipomoea aquatica & 70.10 & 858 & 4 & 1072.50 & 3.26 & 1.43 & 2.25 & 19.44 & 0.45 & 2.38 & 1.42 & 0.6 & 0.75\\
\addlinespace
Ipomoea purpurea & 97.59 & 654 & 6 & 545.00 & 2.27 & 1.24 & 1.88 & 28.23 & 0.58 & 1.06 & 1.57 & 1.0 & 2.74\\
\addlinespace
\rowcolor{gray!6}  Petunia integrifolia & 24.74 & 34657 & 220 & 787.66 & 1.17 & 0.80 & 1.32 & 14.65 & 0.45 & 3.13 & 1.77 & 0.9 & 0.26\\
\addlinespace
Sinapis alba & 33.59 & 3507 & 6 & 3507.00 & 0.55 & 0.63 & 0.91 & 3.62 & 0.77 & 1.98 & 1.07 & 0.7 & 1.12\\
\addlinespace
\rowcolor{gray!6}  Solanum lycopersicum & 22.00 & 28915 & 92 & 1885.76 & 0.09 & 0.19 & 0.35 & 6.47 & 0.31 & 1.16 & 1.13 & 0.7 & 0.48\\
\addlinespace
Solanum melongena & 25.18 & 166989 & 1010 & 992.01 & 1.14 & 0.96 & 1.33 & 11.33 & 0.94 & 4.02 & 3.55 & 1.0 & 1.45\\
\bottomrule
\end{tabu}}
\end{table}

@@

\begin{longtable}[]{@{}lrrrr@{}}
\caption{\textbf{Table S3.} Seed:ovule ratio in percentage for hand
cross-pollination, hand self-pollination, spontaneous selfing and
apomixis for all species.}\tabularnewline
\toprule
\begin{minipage}[b]{0.19\columnwidth}\raggedright
Species\strut
\end{minipage} & \begin{minipage}[b]{0.21\columnwidth}\raggedleft
Hand cross-pollination\strut
\end{minipage} & \begin{minipage}[b]{0.20\columnwidth}\raggedleft
Hand self-pollination\strut
\end{minipage} & \begin{minipage}[b]{0.18\columnwidth}\raggedleft
Spontaneous selfing\strut
\end{minipage} & \begin{minipage}[b]{0.08\columnwidth}\raggedleft
Apomixis\strut
\end{minipage}\tabularnewline
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{0.19\columnwidth}\raggedright
Species\strut
\end{minipage} & \begin{minipage}[b]{0.21\columnwidth}\raggedleft
Hand cross-pollination\strut
\end{minipage} & \begin{minipage}[b]{0.20\columnwidth}\raggedleft
Hand self-pollination\strut
\end{minipage} & \begin{minipage}[b]{0.18\columnwidth}\raggedleft
Spontaneous selfing\strut
\end{minipage} & \begin{minipage}[b]{0.08\columnwidth}\raggedleft
Apomixis\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.19\columnwidth}\raggedright
Brassica oleracea\strut
\end{minipage} & \begin{minipage}[t]{0.21\columnwidth}\raggedleft
32.07\strut
\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedleft
0.00\strut
\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
0.00\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedleft
0\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
Brassica rapa\strut
\end{minipage} & \begin{minipage}[t]{0.21\columnwidth}\raggedleft
44.97\strut
\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedleft
0.00\strut
\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
0.00\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedleft
0\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
Capsicum annuum\strut
\end{minipage} & \begin{minipage}[t]{0.21\columnwidth}\raggedleft
80.00\strut
\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedleft
56.47\strut
\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
19.34\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedleft
0\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
Eruca sativa\strut
\end{minipage} & \begin{minipage}[t]{0.21\columnwidth}\raggedleft
23.75\strut
\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedleft
0.42\strut
\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
0.00\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedleft
0\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
Ipomoea aquatica\strut
\end{minipage} & \begin{minipage}[t]{0.21\columnwidth}\raggedleft
40.00\strut
\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedleft
30.00\strut
\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
20.00\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedleft
0\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
Ipomoea purpurea\strut
\end{minipage} & \begin{minipage}[t]{0.21\columnwidth}\raggedleft
31.67\strut
\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedleft
86.67\strut
\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
31.67\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedleft
0\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
Petunia integrifolia\strut
\end{minipage} & \begin{minipage}[t]{0.21\columnwidth}\raggedleft
80.16\strut
\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedleft
24.77\strut
\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
0.00\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedleft
0\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
Sinapis alba\strut
\end{minipage} & \begin{minipage}[t]{0.21\columnwidth}\raggedleft
41.67\strut
\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedleft
48.33\strut
\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
5.00\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedleft
15\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
Solanum lycopersium\strut
\end{minipage} & \begin{minipage}[t]{0.21\columnwidth}\raggedleft
85.65\strut
\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedleft
41.20\strut
\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
68.48\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedleft
0\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.19\columnwidth}\raggedright
Solanum melongena\strut
\end{minipage} & \begin{minipage}[t]{0.21\columnwidth}\raggedleft
60.48\strut
\end{minipage} & \begin{minipage}[t]{0.20\columnwidth}\raggedleft
74.87\strut
\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
21.56\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedleft
0\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{table}

\caption{\label{tab:unnamed-chunk-4}\textbf{Table S4.} Species x species matrix with the significance of effect “yes” or “no” of the different donors on seed set from the linear mixed effect models. The category of “yes” represents significant effect of the donors (columns) on the different recipient species (rows) and “no” lack of significant reduction of seed set from the control. Significance was tested for all species by comparing with a control of hand cross-pollination with conspecific pollen.}
\centering
\resizebox{\linewidth}{!}{
\fontsize{6}{8}\selectfont
\begin{tabu} to \linewidth {>{\raggedright\arraybackslash}p{2cm}>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedleft}X>{\raggedleft}X}
\toprule
\textbf{X} & \textbf{B..oleracea} & \textbf{B..rapa} & \textbf{E..sativa} & \textbf{S..alba} & \textbf{I..aquatica} & \textbf{I..purpurea} & \textbf{C..annuum} & \textbf{P..integrifolia} & \textbf{S..lycopersicum} & \textbf{S..melongena} & \textbf{S.Significant.effect.of.donors} & \textbf{X..donors.with.significant.effect}\\
\midrule
\rowcolor{gray!6}  B. oleracea &  & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & 9 & 100.0\\
\addlinespace
B. rapa & No &  & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & 8 & 88.9\\
\addlinespace
\rowcolor{gray!6}  E. sativa & Yes & No &  & No & Yes & No & No & No & No & No & 1 & 22.2\\
\addlinespace
S. alba & No & Yes & No &  & Yes & Yes & Yes & No & No & No & 4 & 44.4\\
\addlinespace
\rowcolor{gray!6}  I. aquatica & Yes & Yes & Yes & Yes &  & Yes & Yes & Yes & Yes & Yes & 9 & 100.0\\
\addlinespace
I. purpurea & No & No & Yes & No & No &  & Yes & No & Yes & No & 3 & 33.3\\
\addlinespace
\rowcolor{gray!6}  C. annuum & Yes & Yes & No & Yes & No & Yes &  & Yes & Yes1 & Yes & 7 & 77.8\\
\addlinespace
P. integrifolia & Yes & No & No & Yes & Yes & Yes & No &  & Yes & Yes & 6 & 67.7\\
\addlinespace
\rowcolor{gray!6}  S. lycopersicum & No & Yes & Yes & Yes & Yes & Yes & Yes & Yes &  & Yes & 8 & 88.9\\
\addlinespace
S. melongena & No & Yes & Yes & No & Yes & Yes & Yes & No & No &  & 5 & 55.6\\
\addlinespace
\rowcolor{gray!6}   &  &  &  &  &  &  &  &  &  &  & 60 & 66.7\\
\bottomrule
\end{tabu}}
\end{table}

\begin{longtable}[]{@{}lrrrr@{}}
\caption{\textbf{Table S5.} Output of linear models of the effect of the
different donors on the seed set of each recipient
species.}\tabularnewline
\toprule
& Est. & S.E. & t val. & p\tabularnewline
\midrule
\endfirsthead
\toprule
& Est. & S.E. & t val. & p\tabularnewline
\midrule
\endhead
Petunia integrifolia - (Intercept) & 4.63 & 0.49 & 9.36 &
0.00\tabularnewline
Petunia integrifolia - Brassica oleracea & -1.84 & 0.81 & -2.27 &
0.03\tabularnewline
Petunia integrifolia - Brassica rapa & -0.97 & 0.81 & -1.19 &
0.24\tabularnewline
Petunia integrifolia - Capsicum annuum & 0.78 & 0.81 & 0.96 &
0.34\tabularnewline
Petunia integrifolia - Eruca vesicaria & -0.91 & 0.81 & -1.12 &
0.26\tabularnewline
Petunia integrifolia - Ipomoea aquatica & -3.18 & 0.81 & -3.92 &
0.00\tabularnewline
Petunia integrifolia - Ipomoea purpurea & -4.21 & 0.81 & -5.19 &
0.00\tabularnewline
Petunia integrifolia - Sinapis alba & -2.99 & 0.81 & -3.69 &
0.00\tabularnewline
Petunia integrifolia - Solanum lycopersicum & -2.40 & 0.81 & -2.96 &
0.00\tabularnewline
Petunia integrifolia - Solanum melongena & -2.66 & 0.81 & -3.27 &
0.00\tabularnewline
Solanum lycopersicum - (Intercept) & 4.39 & 0.24 & 18.54 &
0.00\tabularnewline
Solanum lycopersicum - Brassica oleracea & -0.47 & 0.41 & -1.14 &
0.26\tabularnewline
Solanum lycopersicum - Brassica rapa & -2.74 & 0.41 & -6.67 &
0.00\tabularnewline
Solanum lycopersicum - Capsicum annuum & -4.39 & 0.41 & -10.71 &
0.00\tabularnewline
Solanum lycopersicum - Eruca vesicaria & -2.97 & 0.41 & -7.25 &
0.00\tabularnewline
Solanum lycopersicum - Ipomoea aquatica & -4.13 & 0.41 & -10.06 &
0.00\tabularnewline
Solanum lycopersicum - Ipomoea purpurea & -3.80 & 0.41 & -9.27 &
0.00\tabularnewline
Solanum lycopersicum - Petunia integrifolia & -1.82 & 0.41 & -4.44 &
0.00\tabularnewline
Solanum lycopersicum - Sinapis alba & -3.72 & 0.41 & -9.08 &
0.00\tabularnewline
Solanum lycopersicum - Solanum melongena & -1.84 & 0.41 & -4.49 &
0.00\tabularnewline
Solanum melongena - (Intercept) & 6.34 & 0.70 & 9.09 &
0.00\tabularnewline
Solanum melongena - Brassica oleracea & -0.67 & 0.99 & -0.68 &
0.50\tabularnewline
Solanum melongena - Brassica rapa & -4.33 & 0.99 & -4.39 &
0.00\tabularnewline
Solanum melongena - Capsicum annuum & -2.33 & 0.99 & -2.36 &
0.02\tabularnewline
Solanum melongena - Eruca vesicaria & -3.12 & 0.99 & -3.16 &
0.00\tabularnewline
Solanum melongena - Ipomoea aquatica & -6.34 & 0.99 & -6.43 &
0.00\tabularnewline
Solanum melongena - Ipomoea purpurea & -2.71 & 0.99 & -2.74 &
0.01\tabularnewline
Solanum melongena - Petunia integrifolia & -1.43 & 0.99 & -1.45 &
0.15\tabularnewline
Solanum melongena - Sinapis alba & -1.11 & 0.99 & -1.12 &
0.26\tabularnewline
Solanum melongena - Solanum lycopersicum & -0.84 & 0.99 & -0.86 &
0.39\tabularnewline
Capsicum annuum - (Intercept) & 4.59 & 0.52 & 8.78 & 0.00\tabularnewline
Capsicum annuum - Brassica oleracea & -1.80 & 0.74 & -2.43 &
0.02\tabularnewline
Capsicum annuum - Brassica rapa & -2.51 & 0.74 & -3.39 &
0.00\tabularnewline
Capsicum annuum - Eruca vesicaria & -0.63 & 0.74 & -0.85 &
0.40\tabularnewline
Capsicum annuum - Ipomoea aquatica & -1.36 & 0.74 & -1.84 &
0.07\tabularnewline
Capsicum annuum - Ipomoea purpurea & -4.00 & 0.74 & -5.41 &
0.00\tabularnewline
Capsicum annuum - Petunia integrifolia & -4.59 & 0.74 & -6.21 &
0.00\tabularnewline
Capsicum annuum - Sinapis alba & -3.63 & 0.74 & -4.92 &
0.00\tabularnewline
Capsicum annuum - Solanum lycopersicum & -1.52 & 0.74 & -2.06 &
0.04\tabularnewline
Capsicum annuum - Solanum melongena & -3.29 & 0.74 & -4.46 &
0.00\tabularnewline
